\begin{problem}{Werewolf}{standard input}{standard output}{1 second}{256 megabytes}

"The Werewolves" is a popular card game among young people.In the basic game, there are 2 different groups: the werewolves and the villagers.

Each player will debate a player they think is a werewolf or not. 

Their words are like "Player x is a werewolf." or "Player x is a villager.".

What we know is :

1. Villager won't lie.

2. Werewolf may lie. 

Of cause we only consider those situations which obey the two rules above. 

It is guaranteed that input data exist at least one situation which obey the two rules above.

Now we can judge every player into 3 types :

1. A player which can only be villager among all situations, 

2. A player which can only be werewolf among all situations.

3. A player which can be villager among some situations, while can be werewolf in others situations.

You just need to print out the number of type-1 players and the number of type-2 players. 

No player will talk about himself.

\InputFile
The first line of the input gives the number of test cases T.Then T test cases follow.

The first line of each test case contains an integer N,indicating the number of players.

Then follows N lines,i-th line contains an integer x and a string S,indicating the i-th players tell you,"Player x is a S."

limits:

$ 1 \leq T \leq 10 $

$ 1 \leq N \leq 100,000 $

$ 1 \leq x \leq N $

$ S \in $ {"villager"."werewolf"}

\OutputFile

For each test case,print the number of type-1 players and the number of type-2 players in one line,  separated by white space.

\Example

\begin{example}
\exmp{1
2
2 werewolf
1 werewolf
}{0 0
}%
\end{example}

\end{problem}

